Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-06-13 tex/VHzQ.tex
Fixed typo
big, late night update; SHELLQsJ0220-0432

\begin{figure}
  \begin{subfigure}{}\quad
    \centering
    \includegraphics[width=8.5cm]{../light_curves/SHELLQsJ0220-0432LC_20190214.png}
    \caption{The same as Fig.~\ref{fig:MMTJ0215-0529} except for SHELLQs J0220-0432.}
    \label{fig:SHELLQsJ0220-0432}
  \end{subfigure}
  \begin{subfigure}{}\quad
    \centering
    \includegraphics[width=8.5cm]{../light_curves/SDSSJ0959+0227LC_20190612.png}
    \caption{The near infrared light curve for SDSS J0959+0227. Note, 
      SDSS J0959+0227 is too faint in the MIR to be detected by ALLWISE or unnWISE.}
    \label{fig:SDSSJ0959+0227}
  \end{subfigure}
  \medskip
\end{figure}

@@

We thank:
\begin{list}{$\circ$}{}  
\item Mike Read at the ROE WFAU for help with the WFCAM Science Archiv (WSA) and the VISTA Science Archive (VSA). 
\item Bernie Shiao at STScI for help with the Pan-STARRS1 DR1 CasJobs interface. 
\item Aaron Meisner and Eddie Schlafly for facilitating early access to the unWISE Catalog. 
\item Michael Cushing for supplying the Late Type stellar spectra and Beth Biller for useful discussion. 
\end{list}

>>>>

\begin{figure}
  \begin{subfigure}{}\quad
    \centering
    \includegraphics[width=8.5cm]{../light_curves/SHELLQsJ0220-0432LC_20190613.png}
    \caption{The same as Fig.~\ref{fig:MMTJ0215-0529} except for SHELLQs J0220-0432.}
    \label{fig:SHELLQsJ0220-0432}
  \end{subfigure}
  \begin{subfigure}{}\quad
    \centering
    \includegraphics[width=8.5cm]{../light_curves/SDSSJ0959+0227LC_20190612.png}
    \caption{The near infrared light curve for SDSS J0959+0227. Note, 
      SDSS J0959+0227 is too faint in the MIR to be detected by ALLWISE or unnWISE.}
    \label{fig:SDSSJ0959+0227}
  \end{subfigure}
  \medskip
\end{figure}

@@

We thank:
\begin{list}{$\circ$}{}  
\item Mike Read at the ROE WFAU for help with the WFCAM Science Archive (WSA) and the VISTA Science Archive (VSA). 
\item Bernie Shiao at STScI for help with the Pan-STARRS1 DR1 CasJobs interface. 
\item Aaron Meisner and Eddie Schlafly for facilitating early access to the unWISE Catalog. 
\item Michael Cushing for supplying the Late Type stellar spectra and Beth Biller for useful discussion. 
\end{list}
